%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{Klaes Rasmussen -- Résumé} % Print the main header

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Address} \> Vognmandsmarken 24, 2. TV,\\ % Address line 1
\> 2100, København Ø \\ % Address line 2
{\bf Date of Birth} \> 4$^{th}$ October 1987 \\ % Date of birth 
{\bf Nationality} \> Danish % Nationality
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Mobile Phone} \> +45 23 82 06 82 \\ % Mobile phone
{\bf Email} \> \href{mailto:k@klaes.dk}{k@klaes.dk} \\ % Email address
\end{tabbing}}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\section{Personal Profile}

I am a happy, smiling person who likes games, puns and neat code. I love doing frontend work
and trying out new methods and technologies. 
Therefore I have a hobby of reading about the latest developments in JavaScript
and playing computer games.

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Employment History}

\job
{Aug 2016 -}{Nov 2016}
{Alpha Solutions A/S, Gothersgade 14, 4th floor, 1123 Copenhagen K, Denmark}
{http://www.alpha-solutions.dk/}
{Developer / Build script expert}
{Working with Demandware and setting up build scripts both locally and on TeamCity server.\\
\rule{0mm}{5mm}\textbf{Technologies:} Node.js, Demandware, JavaScript, Windows Powershell}

%------------------------------------------------

\job
{Oct 2015 -}{Aug 2016}
{OMI A/S, Amaliegade 4, 1256 Copenhagen, Denmark}
{http://www.omi.dk}
{Developer}
{Creating and maintaining Citroën campaign websites for Norway, Sweden and Denmark.\\
Creating most of the frontend, written in either PHP or JavaScript with React, while using Node.js 
for library management.\\
All while ensuring that the corresponding backend was kept in working condition with PHP and Symfony 2. 
Creating and maintaining auto deploy scripts.\\
\rule{0mm}{5mm}\textbf{Technologies:} Node.js, JavaScript, React, CSS, SASS, git, HTML, Less, shell scripts, PHP, (React-Redux)}

\job
{Nov 2014 -}{July 2015}
{Univerity of Copenhagen, Karen Blixens Vej 4, 2300 Copenhagen S, Denmark}
{http://inss.ku.dk/}
{Student Worker - Developer}
{Creating a frontend and backend for comparing the use of input sentences or words statistically. 
Frontend of very simple HTML and php framework for showing my Python backend data.
Created various graphs to show distribution of input sentences over time, age and gender. 
Also a heatmap for showing sentence usage in NUTS-regions. All using a set of large CSV input files from several countries. 
Countries were compared separately. 
I parsed the data and inserted it into a SOLR database, then using that in conjunction with Python to generate the graphs and map. 
Even made it relatively fast :D (around 1 sec to do map of england with 500,000 results, heatmap generated and shown in browser)

https://github.com/klaesra/WordlyExplorer \\
\rule{0mm}{5mm}\textbf{Technologies:} Python, Apache Solr, PHP, HTML, CSS}

\job
{2010 -}{2013}
{Various places}
{}
{Student jobs}
{Various support jobs for phone and internet companies. Webmaster on a Wordpress site for a while.}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\tabbedblock{
\bf{2014-2015} \> First year of master in It and Cognition - \href{http://studies.ku.dk/masters/it-and-cognition/}{Language Department, University of Copenhagen} \\[5pt]
\>\+
}

%------------------------------------------------

\tabbedblock{
\bf{2006-2013} \> BSc in Computer Science - \href{http://www.diku.dk}{Department of Computer Science, University of Copenhagen} \\[5pt]
\>\+
}

%------------------------------------------------

\tabbedblock{
\bf{2003-2006} \> International Baccaulaureate - \href{http://osc.lk/school/secondary-school/ib-deploma/}{Overseas School of Colombo, Sri Lanka}\\[5pt]
\>\+
\textit{Higher level Mathematics} \> A \\
\textit{Higher level Physics} \> A \\
\textit{Higher level Economics} \> A
}


%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Software Engineering Skills}

\skillgroup{Web Development}
{
\textit{HTML5, CSS3/SASS, JavaScript/React}\\
\textit{Node.js, Gulp, Grunt}
}

%------------------------------------------------

\skillgroup{Programming Languages}
{
\textit{Python}\\
\textit{PHP}\\
\textit{JavaScript}\\
\textit{Latex}\\
\textit{Go}\\
\textit{shell script}
}

%------------------------------------------------

\skillgroup{Miscellaneous}
{
\textit{Apache Solr} - database\\
\textit{MySQL}\\
\textit{SVN, git} - source version control
}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interests}

\interestsgroup{
\interest{Golfing}
\interest{Travelling}
\interest{Dancing}
\interest{Acting}
\interest{Singing}
\interest{Computers}
\interest{Computer games}
\interest{JavaScript evolution}
}

\end{document}