%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{Klaes Ellyton }{Rasmussen}{frontend/fullstack developer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
Vognmandsmarken 24, 2.TV
2100 København Ø
Denmark
~
+45 23820682
~
\href{mailto:k@klaes.dk}{k@klaes.dk}
\section{languages}
danish mother tongue
english mother tongue
norwegian/swedish
french basic
\section{programming}
{\color{red} $\varheartsuit$} JavaScript, TypeScript
Angular 2+, React
Node.js, CSS3, HTML5
Python \& etc.
\end{aside}




%----------------------------------------------------------------------------------------
%	INTRODUCTION SECTION
%----------------------------------------------------------------------------------------

\section{introduction}

I am a happy, smiling person who likes games, puns and neat code. I love doing frontend work
and trying out new methods and technologies. 
Therefore I have a hobby of reading about the latest developments in JavaScript
and playing computer games.

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}

%------------------------------------------------

\entry
{Mar 2017 $\rightarrow$ \\ Now}
{Solteq}
{Copenhagen}
{\emph{frontend developer} \\
Working as the only pure frontend dev with Angular 2+. Working closely with customer Apotek 1 from Norway, and their chosen designer group. My focus is on developing the intricate parts of their frontend for both B2C and B2B solutions. I provide ample knowledge, ideas for improvements both for UX and DX.
\begin{itemize}
\item Learned how to work with WCS (IBM Websphere Commerce Solutions) as a backend
\item Learned the ups and downs of Angular 2+ as both a middleware and a frontend solution:
\begin{itemize}
\item Typescript programming all the way
\item Working with Jasmine and Karma as test-suite
\item Angular for native and web-apps
\end{itemize}
\item Main developer on B2C checkout page (apart from design)
\item Main developer on B2B account pages, asked to change design where it was dysfunctional
\end{itemize}}

\entry
{Aug 2016 $\rightarrow$ \\ Nov 2016}
{Alpha Solutions A/S}
{Copenhagen}
{\emph{developer / build script expert} \\ 
Working with Demandware and setting up build scripts both locally and on TeamCity server.
\begin{itemize}
\item Learned to work with Salesforce Commerce Cloud
\item Working with JavaScript, grunt scripts and Windows Powershell
\end{itemize}
}

\entry
{Oct 2015 $\rightarrow$ \\ Jul 2016}
{OMI A/S}
{Copenhagen}
{\emph{Developer} \\
Creating and maintaining Citroën campaign websites for Norway, Sweden and Denmark.
Creating most of the frontend, written in either PHP or JavaScript with React, while using Node.js 
for library management.
All while ensuring that the corresponding backend was kept in working condition with PHP and Symfony 2. 
Creating and maintaining auto deploy scripts.\\
\begin{itemize}
	\item Learned to work with React, JavaScript, Node.js, CSS, SASS, Less, HTML5
	\item Got better with PHP, shell scripts, git
\end{itemize}
}

%------------------------------------------------

\end{entrylist}

\pagebreak

\subsection{Part Time}

\begin{entrylist}

\entry
{Aug 2015 $\rightarrow$ \\ Oct 2015}
{getQueried}
{Copenhagen}
{\emph{Part time developer} \\
I got a chance to try programming for a start up, we developed in Google Go. Job was unpaid and shortly after I got an offer to work for OMI.
}

\entry
{Nov 2014 $\rightarrow$ \\ Jul 2015 }
{University of Copenhagen}
{Copenhagen}
{\emph{Student Worker - Developer} \\
Creating a frontend and backend for comparing the use of input sentences or words statistically. 
Frontend of very simple HTML and php framework for showing my Python backend data.
Created various graphs to show distribution of input sentences over time, age and gender. 
Also a heatmap for showing sentence usage in NUTS-regions. All using a set of large CSV input files from several countries. 
Countries were compared separately. 
I parsed the data and inserted it into a SOLR database, then using that in conjunction with Python to generate the graphs and map. 
Even made it relatively fast :D (around 1 sec to do map of england with 500,000 results, heatmap generated and shown in browser)

https://github.com/klaesra/WordlyExplorer \\
\begin{itemize}
	\item Learned to work independantly on a larger project over a longer period of time
	\item Learned a lot about scripting and Python and data transfer between different platforms
\end{itemize}
}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2014 $\rightarrow$ \\ 2015}
{Master {\normalfont in It and Cognition}}
{Language Department, University of Copenhagen}
{Completed the first year of the master, after which there was no more programming and I moved onto jobs.}

%------------------------------------------------

\entry
{2006 $\rightarrow$ \\ 2013}
{Bachelor {\normalfont in Computer Science}}
{Department of Computer Science, University of Copenhagen}
{}

%------------------------------------------------

\entry
{2003 $\rightarrow$ \\ 2006}
{International Baccaulaureate}
{Overseas School of Colombo, Sri Lanka}
{\textit{Higher level Mathematics} \\
\textit{Higher level Physics} \\
\textit{Higher level Economics} }

%------------------------------------------------

\end{entrylist}



%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} UX, DX, JavaScript, TypeScript, web design, web app creation, efficiency, code cleanliness, maintainability, deterministic code \\
\textbf{personal:} surfing, golfing, travelling, dancing, acting, singing, computers, computer games, quantum computing


\end{document}